Deep learning on psychological arousal classification

### 2015-05-07 paper/paper.tex

The data was processed with %TODO: asdfasdfasdf how did siegle process the data??
%TODO: we have big data, oooh. okay maybe not that big but it still takes forever to load 
%-Dataset (details)
% -processing
%-Features
% -raw
% -dtft
%  -windows
% -wavelets
% -other

>>>>

The dataset was collected with Emotiv EPOC EEG devices. The EEG data has 14 channels at 128Hz.  The data was processed with %TODO: asdfasdfasdf how did siegle process the data??

We post-processed the resulting 128Hz signal with DFT and wavelets. We used 5 channel DFT threshholding at 0.1Hz, 4Hz, 8Hz, 12Hz, 30Hz, and 64Hz. We used Debauchey wavelets, trying a variety of wavelet decomposition depths. We also derived a number of features based on the feature set used in recent work of (citation needed) which includes eigen correlation, statistical moments, and Hjorth parameters.
%TODO: we have big data, oooh. okay maybe not that big but it still takes forever to load 
%-Dataset (details)
% -processing
%-Features
% -raw
% -dtft
%  -windows
% -wavelets
% -other
